---
title: "Practic3 M1"
author: "Victor Tang"
date: "2021/12/24"
output: html_document
---
```{r}
library(vegan)
library(ade4)
library(gclus)
library(qgraph)
library(factoextra)
library(fpc)
library(ggplot2)
library(gridExtra)
library(e1071)
library(corrplot)
library(tree)
library(rpart)
library(rattle)
library(randomForest)
library(caret)
library(devtools)
library(mvabund)
library(dplyr)
library(gclus)
```
Open the dataset "Tikus", from the package "mvabund". The tikus dataset is a list consist of 2 list, one is the species abundance (60 observations * 75 variables) data frame, and the x (year) (60*2 data frame).
```{r}
data(tikus)
tikus
head(tikus)
str(tikus)
```
Separate the two data frames. Add a column "year" in the abundance data frame from x (year). Select the observations in the year 1981, 1983 and 1985 (81, 83, 85), finally remove the year column. Here is the prepared dataset for our analysis.
```{r}
sp_abu <- tikus$abund
year <- tikus$x

sp_abu$time <- year$time
selected <- sp_abu  %>%
  filter(year == 81 | year == 83 | year == 85)

selected$time <- NULL
selected
```
Use the function vegdist() from the package "vegan", to create a Bray-Curtis dissimilarity matrix.
```{r}
selected.bc <- vegdist(selected, method = "bray")
selected.bc
```
The matrix is visualised into a heatmap, as the coldiss() function from the package "gclus" is not working, therefore I copied a coldiss function from online, to produce the heatmap
```{r}
coldiss <- function(D, nc = 4, byrank = TRUE, diag = FALSE)
{
  require(gclus)
  
  if (max(D)>1) D <- D/max(D)
  
  if (byrank) {
    spe.color <- dmat.color(1-D, cm.colors(nc))
  }
  else {
    spe.color <- dmat.color(1-D, byrank=FALSE, cm.colors(nc))
  }
  
  spe.o <- order.single(1-D)
  speo.color <- spe.color[spe.o, spe.o]
  
  op <- par(mfrow=c(1,2), pty="s")
  
  if (diag) {
    plotcolors(spe.color, rlabels=attributes(D)$Labels, 
               main="Dissimilarity Matrix", 
               dlabels=attributes(D)$Labels)
    plotcolors(speo.color, rlabels=attributes(D)$Labels[spe.o], 
               main="Ordered Dissimilarity Matrix", 
               dlabels=attributes(D)$Labels[spe.o])
  }
  else {
    plotcolors(spe.color, rlabels=attributes(D)$Labels, 
               main="Dissimilarity Matrix")
    plotcolors(speo.color, rlabels=attributes(D)$Labels[spe.o], 
               main="Ordered Dissimilarity Matrix")
  }
  
  par(op)
}


coldiss(selected.bc, byrank=F,diag=T)

```

Transpose the data frame by t(), produce a Jaccard dissimilarity matrix using vegdist, data are binary transformed. qgraph() to produce the network of species co-occurence.
```{r}
selected.t.bi <- vegdist(t(selected),'jac', binary=T)
qgraph(1-selected.t.bi, layout='spring', vsize=4)
```




