---
title: "ttest_modified"
author: "Victor Tang"
date: "2021/12/8"
output: html_document
---

Read dataset "rairuoho"
```{r}
rairuoho<-read.table('https://www.dipintothereef.com/uploads/3/7/3/5/37359245/rairuoho.txt',header=T, sep="\t", dec=".")

```

The t.test function designed for two samples, for paired or non-paired samples. For paired samples, it will go to the set of paired test formula; for unpaired one, there are two sets where equal or unequal population variance.  
```{r}
ttest <- function(A, B, paired = c('TRUE', 'FALSE'), mu, var.equal = c('TRUE', 'FALSE', "NA")){
  if(paired == TRUE){ 
  C <- A - B
  t_value=((sum(A)-sum(B)-mu)/length(A))/(sd(C)/length(A)^0.5)
  df = length(A)-1
  p= pt(t_value, df, lower.tail = T)
  paste('t=', t_value, ', degree_of_freedom=', df, ' , p = ', p)
  }
  else{if(var.equal == TRUE){
    psv = ((length(A)-1)*var(A)+(length(B)-1)*var(B))/(length(A)+length(B)-2)
    t_value = (mean(A)-mean(B))/(psv((1/length(A))+(1/(length(B)))))
    df= length(A)+length(B)-2
    p= pt(t_value, df, lower.tail = T)
    paste('t=', t_value, ', degree_of_freedom=', df, ' , p = ', p)
  }else{
    t_value = (mean(A)-mean(B))/((var(A)/length(A)+var(B)/length(B))^0.5)
  df=((var(A)/length(A)+var(B)/length(B))^2)/( (var(A)/length(A))^2/(length(A)-1)+ (var(B)/length(B))^2/(length(B)-1) )
  p= pt(t_value, df, lower.tail = T)
  paste('t=', t_value, ', degree_of_freedom=', df, ' , p = ', p)
  }
  }
}
```

Read the samples we want to test, in this case, I want to compare the same individual without nutrient treatment (water), it they have grow bigger or not, so use paired t test (paired = TURE)
```{r}
library(dplyr)

D3<-rairuoho%>%select(day3, treatment)%>%filter(treatment=="water")
D7<-rairuoho%>%select(day7, treatment)%>%filter(treatment=="water")

```

test 
```{r}
ttest(D3$day3, D7$day7, paired = TRUE, 0, NA)
```

To check my answer by the t.test() in r
```{r}
t.test(D3$day3, D7$day7, paired = TRUE)
```